On selection of a coupling method to cope with change of priors in one-vs-one classification

### 2025-06-16 experiment.tex

These questions will be put to test in Sections \ref{sec:exp1}, \ref{sec:exp2}, and \ref{sec:exp3}.

\subsection{Experiment: Accuracy of canonical coupling methods on benchmark datasets} \label{sec:exp1}

@@

\subsection{Experiment: A parametric family of Bayes covariant methods}

@@

\subsection{Experiment: Effect of change of priors}  \label{sec:exp3}
%\subsection{Wu-Lin-Weng's method}

>>>>

These questions will be put to test in Sections \ref{sec:exp1} --\ref{sec:exp4}.

\subsection{Experiment: Accuracy of canonical coupling methods} \label{sec:exp1}

@@

\subsection{Experiment: A parametric family of Bayes covariant methods}
\label{sec:exp3}

@@

\subsection{Experiment: Effect of change of priors}  \label{sec:exp4}
%\subsection{Wu-Lin-Weng's method}

We have shown that are situations when Wu-Lin-Weng's method outperforms even the best Bayes-covariant parametric methods. In this section we thus ponder the question whether some non-Bayes covariant method would be more resilients to change of priors. We consider two facets to this question.

Let us start with some notation. Consider a classification method $\boldsymbol{c}_0$ based on coupling. Suppose the priors change, and let us denote by $\boldsymbol{c}_1$ the classification model where we apply \eqref{eq:changePrior} to binary classifiers, and by $\boldsymbol{c}_2$ the classification method when we apply \eqref{eq:changePrior} after coupling.

The first question is whether for some coupling method the difference in predictions between $\boldsymbol{c}_1$ and $\boldsymbol{c}_2$ would be smaller. The results are shown in Table \ref{tab:exp4}.

\input tab-exp4.tex

The second question is whether a coupling method would more consistently provide true answers. Let us remark that Assumption 1 is inconsistent with ground truth being certain. But we may
